Polka-dotted Stars: Mapping the Surface of HAT-P-11

### 2023-08-15 src/tex/ms.tex
added a table

\subsection{Short light curve}
For our initial experiment with minimal complexity, we created a synthetic light curve that involved a single planetary transit (therefore, 
\emph{a short light curve}). Here, we examined two distinct sampling techniques: No-U-Turn Sampling (NUTS) using \texttt{pymc3} and Markov Chain Monte Carlo (MCMC) 
using \texttt{emcee}. The MCMC technique exhibited a faster convergence rate of the walkers, despite the fact that it still required a significant amount of time.
\subsection{Long light curves (multiple transits)}
\section{Results and Discussion}

>>>>

\subsection{Short light curve}
For our initial experiment with minimal complexity, we created a synthetic light curve that involved a single planetary transit (therefore, 
\emph{a short light curve}). Here, we examined two distinct sampling techniques: No-U-Turn Sampling (NUTS) using \texttt{pymc3} and Markov Chain Monte Carlo (MCMC) 
using \texttt{emcee}. The MCMC technique exhibited a faster convergence rate of the walkers, despite the fact that it still required a significant amount of time.
\subsection{Long light curves (multiple transits)}

\begin{table}[]
    \label{tab:LongPriors}
    \caption{The free parameters for the synthetic data, their true values, and their priors.}
    \begin{tabular}{lll}
    \hline
    Parameter                                 & True value            & Prior distribution    \\ \hline\hline
    $i_p$                                     & $90^\circ$            & Planetary Inclination \\
    $e$                                       & $0.0$                 & Uniform               \\
    $P$                                       & $4.887802443$         & Period                \\
    $t_0$                                     & $0.0$                 & Uniform               \\
    $R_p$                                     & $0.02732$             & Logarithmic           \\
    $m_p$                                     & $0.81 \times 10^{-3}$ & Uniform               \\ \hline
    $i_\star$                                 & $90^\circ$            & Stellar Angle         \\
    $\lambda$                                 & $30^\circ$            & Stellar Angle         \\
    $P_\star$                                 & $30$                  & Period                \\ \hline
    $r$                                       & $20^\circ$            & Uniform               \\
    $c$                                       & $0.5$                 & Uniform               \\
    $n$                                       & 1                     & Uniform               \\
    $\mu_\phi$                                & 30                    & Uniform               \\
    $\sigma_\phi$                             & 5                     & Uniform               \\ \hline
    \end{tabular}
    \end{table}

\section{Results and Discussion}
